Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity

### 2025-09-26 paper_short_in_one.tex
update auto-generated file paper_short_in_one.tex

Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 187~/~373). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.

Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.

@@

The Challenge score of our team ``Revenger'' on the hidden validation set was 0.245, ranking 187th among 373 submissions. The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.

\begin{table}[!htp]
\centering
\begin{tabular}{r|r|r|r}
Training          & Validation & Test & Ranking   \\ \hline
$0.451 \pm 0.005$ & 0.245      & TBA  & 187~/~373 \\ \hline
\end{tabular}
\caption{Challenge scores for our submitted entries (team ``Revenger''). Training: internal hold-out mean $\pm$ std over repeated runs. Validation: best among 10 validation submissions. Test: to be announced. Ranking: position on the hidden validation leaderboard.}
\label{tab:scores}
\end{table}

>>>>

Results: On the hidden validation set, our method received a Challenge score of 0.163 (rank 32~/~40). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.

Conclusion: The proposed method demonstrates effective performance for ECG-based Chagas screening, highlighting its potential for improving detection accuracy and reliability in resource-limited scenarios.

@@

The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 teams eligible for rankings. The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.

\begin{table}[!htp]
\centering
% \input{tables/official_phase_results}
\begin{tabular}{r|r|r|r}
Training          & Validation & Test & Ranking   \\ \hline
$0.451 \pm 0.005$ & 0.245      & 0.163  & 32~/~40 \\ \hline
\end{tabular}

\caption{Challenge scores for our submitted entries (team ``Revenger''). Training: internal hold-out mean $\pm$ std over repeated runs. Validation: best among 10 validation submissions. Test: to be announced. Ranking: position on the hidden validation leaderboard.}
\label{tab:scores}
\end{table}
